CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2019-02-14 gpus/paper.tex
add ref
add paper
add a code
fix figure
add an author list

\author{Castro developers / M.~P.~Katz et al.}
\affil{}
\email{}

@@

Existing GPU-enabled astrophysical hydro codes include
\citet{gamer,cholla,fargo3d,pekkila:2017}

@@

@@

\begin{figure}
\centering
\includegraphics[height=0.25\textheight]{gpu_1} \\
\includegraphics[height=0.25\textheight]{gpu_2} \\
\includegraphics[height=0.25\textheight]{gpu_3}
\caption{\label{fig:loops} caption}
\end{figure}

>>>>

\correspondingauthor{Michael Zingale}

\collaboration{the Castro Development Team}

\author[0000-0003-2103-312X]{Ann S. Almgren}
\affil{Center for Computational Sciences and Engineering, Lawrence Berkeley National Laboratory}

\author[0000-0002-3185-9809]{Maria Barrios Sazo}
\affil{Department of Physics and Astronomy, Stony Brook University}

\author{Kevin Gott}
\affil{National Energy Research Scientific Computing Center}

\author[0000-0002-1530-781X]{Alice Harpole}
\affil{Department of Physics and Astronomy, Stony Brook University}

\author[0000-0003-0439-4556]{Max P.~Katz}
\affil{NVIDIA Corporation}

\author[0000-0003-2300-5165]{Donald Willcox}
\affil{Center for Computational Sciences and Engineering, Lawrence Berkeley National Laboratory}

\author[0000-0001-8092-1974]{Weiqun Zhang}
\affil{Center for Computational Sciences and Engineering, Lawrence Berkeley National Laboratory}

\author[0000-0001-8401-030X]{Michael Zingale}
\affil{Department of Physics and Astronomy, Stony Brook University}
\email{michael.zingale@stonybrook.edu}

@@

Existing GPU-enabled astrophysical hydro codes include
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018}

@@

\section{The Castro hydrodynamics code}

Disucss changes since last paper

Discuss open development model

@@

\begin{figure*}
\centering
\includegraphics[width=0.3\textwidth]{gpu_1} 
\includegraphics[width=0.3\textwidth]{gpu_2} 
\includegraphics[width=0.3\textwidth]{gpu_3}
\caption{\label{fig:loops} caption}
\end{figure*}
